Individual and Differential Harm in Redistricting

### 2022-04-10 paper/paper.Rmd
checkpoint

Differential partisan harm identifies each gerrymander as such, with a large negative value for the Democratic gerrymander and a large positive value for the Republican gerrymander.
These values are relatively directly interpretable; for example, the differential harm score of $-0.22$ means that an average Democratic voter is 22% less likely to be misrepresented than their average Republican counterpartisan.
The efficiency gap and declination measures also correctly identify the gerrymanders, though they are much more discrete, and declination gives a much larger score in absolute value to the Democratic plan than to the Republican.
In contrast, the partisan bias and mean-median measures incorrectly classify the Republican gerrymander as a fair plan and a Democratic-leaning outlier.
These measures are weakly correlated with the expected number of Democratic seats, and show substantial variation even for fixed values of total seats won at baseline.

>>>>

Differential partisan harm identifies each gerrymander as such, with a large negative value for the Democratic gerrymander and a large positive value for the Republican gerrymander.
These values are relatively directly interpretable; for example, the differential harm score of $-0.221$ means that an average Democratic voter is 22.1% less likely to be misrepresented than their average Republican counterpartisan.
The efficiency gap and declination measures also correctly identify the gerrymanders, though they are much more discrete, and declination gives a much larger score in absolute value to the Democratic plan than to the Republican.
In contrast, the partisan bias and mean-median measures incorrectly classify the Republican gerrymander as a fair plan and a Democratic-leaning outlier.
These measures are weakly correlated with the expected number of Democratic seats, and show substantial variation even for fixed values of total seats won at baseline.
